Neon: Nuclear Norm to Beat Muon

### 2025-05-06 poster/neon_poster.tex
Updated the poster

\usepackage[papersize={38in,28in}]{geometry}

@@

\hrule\medskip
\Head{MLP tests}\\
Couple of sentences and a vector(!) picture (reference picture for now).
\begin{figure}[h]
    \center{\includegraphics[width=0.8\linewidth]{../figs/mlp24/accuracy_vs_epochs_simple.png}}
    \caption{MLP validation loss}
    \label{fig:mlp_loss}
\end{figure}

@@

\begin{textblock}{7.0}(16,1.5)

\hrule\medskip
\Head{CIFAR10 tests}\\
Couple of sentences and a vector(!) picture (reference picture for now).
\begin{figure}[h]
    \center{\includegraphics[width=0.8\linewidth]{../figs/mlp24/accuracy_vs_epochs_moderate.png}}
    \caption{CIFAR10 validation loss}
    \label{fig:cifar10_loss}
\end{figure}

>>>>

%\usepackage{svg}
\usepackage[papersize={38in,28in}]{geometry}

@@

\hrule\medskip
\Head{MLP tests}\\
We test Muon, SGD, and Neon on a simple MLP (2 linear layers) that solves CIFAR-10 classification problem. Muon converges faster than Neon and reaches higher accuracy.
\begin{figure}[h]
    \center{\includegraphics[width=0.8\linewidth]{../figs/mlp0605/loss_vs_epochs_mlp.pdf}}
    \caption{MLP validation loss}
    \label{fig:mlp_loss}
\end{figure}

@@

\begin{textblock}{7.0}(16,1.5)
    \begin{figure}[h]
        \center{\includegraphics[width=0.8\linewidth]{../figs/mlp0605/accuracy_vs_time_mlp.pdf}}
        \caption{MLP Accuracy vs wallclock time}
        \label{fig:mlp_loss}
    \end{figure}

\hrule\medskip
\Head{CIFAR-10 tests}\\
Now we compare Muon and Neon on ResNet from Keller's cifar10-aribench at GitHub. On RTX-4050, Muon is approximately twice as fast as Neon. Moreover, Neon has a strange dependency on batch size that has not been observed for Muon: smaller batch size 500 leads to accuracy 84\% in eight epochs, while batch size 2000 results in only 51\%.

TO-DO: we conduct experiments like those with MLP, and add plots here.
